Formalizing Stack Safety as a Security Property

### 2023-02-04 submission5/core.tex
Fix

\proposecut{In \cref{sec:example} we give such an instantiation, and
  use it to illustrate our security properties.  But we stress that
  the property definitions themselves are independent of the
  instantiation.}

>>>>

\bcp{cut this?}In \cref{sec:example} we give such an instantiation, and
  use it to illustrate our security properties.  But we stress that
  the property definitions themselves are independent of the
  instantiation.
